Workflow

### 2014-11-30 Workflow/Workflow.Rmd
Updated location of r-versions script.
Updated Workflow.R about Sources. PostProcess.R now accepts multiple Sources.

### Create the batch script
* Run the script `r-versions` on `dahl` to see which nodes are operational and which nodes have a working version of `R`.
* Create the file `Scripts/<Source>_batch.bash` file.
    + It is probably best to modify an existing `<Source>_batch.bash` file.      
    + Be sure to edit the `$SRC` variable.
    + Distribute the work over the nodes in a way that makes sense.
    + Avoid non-working nodes or nodes that have an out-of-date version of `R` as revealed by `r-versions`.
* Push the `<Source>_batch.bash` file to GitHub.
* On `acc`, pull from GitHub.

@@

### Post-process the results
* Run `Scripts/PostProcess.R -S <Source>` on a node of `dahl` to create:       
    + `data_postprocessed/<Source>_Coeffs.rda` and
    + `data_postprocessed/<Source>_Fitted.rda`.         
* Note that this command must be issued from a node of the cluster (e.g., `node-00`), not from `fs1.calvin.edu`.
`fs1` does not have a full install of `R`.

>>>>

### Create the batch script
* Run the script `r-versions` on `dahl` to see which nodes are operational and which nodes have a working version of `R`. (This script is located at `/usr/local/bin/r-versions`.)
* Create the file `Scripts/<Source>_batch.bash` file.
    + It is probably best to modify an existing `<Source>_batch.bash` file.      
    + Be sure to edit the `$SRC` variable.
    + Distribute the work over the nodes in a way that makes sense.
    + Avoid non-working nodes or nodes that have an out-of-date version of `R` as revealed by `r-versions`.
* Push the `<Source>_batch.bash` file to GitHub.
* On `acc`, pull from GitHub.

@@

### Post-process the results
* Run `Scripts/PostProcess.R -S <Source>` on a node of `dahl` to create:       
    + `data_postprocessed/<Source>_Coeffs.rda` and
    + `data_postprocessed/<Source>_Fitted.rda`.  
* `PostProcess.R` will accept multiple `<Source>`s. E.g., `Scripts/PostProcess.R -S IST,Leeds,SUN,REXS1960`
* Note that this command must be issued from a node of the cluster (e.g., `node-00`), not from `fs1.calvin.edu`.
`fs1` does not have a full install of `R`.
